---
title: "Social Survey 2010"
author: "Christian Celis"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyvertse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Use the data from the 2010 general social survey to explore whether belief in continental drift (condrift), views on capitol punishment (cappun), and race (race) are independent of each other.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
alldata <- read.csv(file="gss2010.csv", header=TRUE)
#names(alldata)
```


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
First we will look at a barchart and compare race with the belief of continental drift

```{r}
barchartGC(~race+condrift, data=alldata, type = "percent") 
```
  
Here we can see that there is no major difference in comparing the beliefs of whites compares to others. However, lookin at whites compared to the beliefs of blacks there is a major difference. 


  
Now we will compare races with the belief of capital punishment.


```{r}
barchartGC(~race+cappun, data=alldata, type = "percent") 
```
  
Looking at the results of the barchart we can see that by comparing the beliefs of whites against black and other, there is a significant differnce. Not much of a difference when comparing black with other.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
tab1 = xtabs(~race+condrift, data=alldata)
rowPerc(tab1)
colPerc(tab1)
```

```{r}
tab2 = xtabs(~race+cappun, data=alldata)
rowPerc(tab2)
colPerc(tab2)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(tab1, graph = TRUE) 
```
```{r}
chisqtestGC(tab2, graph = TRUE) 
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
